Classification and Regression on Random Dot Product Graphs

### 2024-01-12 draft.Rmd
minor updates

$$
\begin{aligned}
\|T b - \hat{T} \hat{b} W\|_{2,\infty} & = \|T b - \hat{T} \hat{b} W + \hat{T} b - \hat{T} b\|_{2,\infty} \\
& = \|(T - \hat{T}) b - \hat{T} (\hat{b} W - b)\|_{2,\infty} \\
& \leq \|(T - \hat{T}) b\|_{2,\infty} + \|\hat{T} (\hat{b} W - b)\|_{2,\infty} \\
& \leq \|T - \hat{T}\|_{2,\infty} \|b\|_F + \|\hat{T}\|_{2,\infty} \|b - \hat{b} W\|_F \\
& \stackrel{p}{\to} 0.
\end{aligned}
$$
$\|b\|_F$ and $\|\hat{T}\|_{2,\infty}$ are finite, so both $\|T - \hat{T}\|_{2,\infty}$ and $\|b - \hat{b} W\|_F$ must converge to $0$ in probability. 
\end{proof}

>>>>

$$
\begin{aligned}
\|T b - \hat{T} \hat{b} W\|_{2,\infty} & = \|T b - \hat{T} \hat{b} W + \hat{T} b - \hat{T} b\|_{2,\infty} \\
& = \|(T - \hat{T}) b - \hat{T} (\hat{b} W - b)\|_{2,\infty} \\
& \leq \|(T - \hat{T}) b\|_{2,\infty} + \|\hat{T} (\hat{b} W - b)\|_{2,\infty} \\
& \leq \|T - \hat{T}\|_{2,\infty} \|b\|_F + \|\hat{T}\|_{2,\infty} \|b - \hat{b} W\|_F.
\end{aligned}
$$
Since $\|T b - \hat{T} \hat{b} W\|_{2,\infty} \stackrel{p}{to} 0$, $\|T - \hat{T}\|_{2,\infty} \|b\|_F + \|\hat{T}\|_{2,\infty} \|b - \hat{b} W\|_F \stackrel{p}{\to} 0$. 
Then since $\|b\|_F$ and $\|\hat{T}\|_{2,\infty}$ are finite, both $\|T - \hat{T}\|_{2,\infty}$ and $\|b - \hat{b} W\|_F$ must converge to $0$ in probability. 
\end{proof}
